R for Clinical Study Reports and Submission

### 2021-09-21 tlf-disposition.Rmd
Update tlf-disposition.Rmd

In the code below, we calculate the number and percentage of participants who discontinued the study for different reasons.
For display purposes, we use `paste0("    ", row)` to add leading spaces to mimick identation in the final report.

@@

In the below code, formatting of the final table is defined. 
We highlighted items that is not discussed in the previous discussion.

>>>>

In the code below, we calculate the number and percentage of participants who discontinued the study for different reasons.
For display purposes, `paste0("    ", row)` is used to add leading spaces to mimick identation in the final report.

@@

In the below code, formatting of the final table is defined. 
Items that were not discussed in the previous sections, are highlighted below.
